Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-25 paper/paper.tex
pass related work
running time

\textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.}
%%  \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
%%  evolutionaries approaches to 
%% autonomously generate rules using the Snort IDS. They built 
%% their own ICMP datasets by using packet creation tools or by capturing network traffic. 
%% Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
%% for non-ICMP attacks.
%% 
%% Vollmer created ten different packets to match ten existing rules, and then used 
%% these packets as input to the rule generation process. As a result, the produced 
%% rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.
%% 
%% Guruprasad manually created a set of rules by analyzing the network patterns and 
%% the datasets, this set of rules was used as the initial population of the algorithm. 
%% The produced rules achieved a detection rate up to 96\%, the false positive rate 
%% was not evaluated. 
%% 
%% On our experiments with Syrius, we used a total of \totalPackets packets that 
%% matches \totalAttacks different existing rules and it was able to generate rules that detected 
%% all the packets with no false positives.  
%%  }  
\subsubsection{Running time}\Mar{}

@@

\Gui{Ganesan \etal{} introduces an idea of generating new sets of rules based on modifications of existing rules. They used the community edition of snort rules from 2012 for the modifications and tested with the the pcap file from the MACCDC 2012 dataset. It was reported an increase in the number of alerts, but it wasn't analysed the false alarmrates for abduced rules. Their technique is parallel to the rule creation strategies, as the objective of the modified rules is to capture variations and evolutions of attacks.}

>>>>

\textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.}
%%  \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
%%  evolutionaries approaches to 
%% autonomously generate rules using the Snort IDS. They built 
%% their own ICMP datasets by using packet creation tools or by capturing network traffic. 
%% Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
%% for non-ICMP attacks.
%% 
%% Vollmer created ten different packets to match ten existing rules, and then used 
%% these packets as input to the rule generation process. As a result, the produced 
%% rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.
%% 
%% Guruprasad manually created a set of rules by analyzing the network patterns and 
%% the datasets, this set of rules was used as the initial population of the algorithm. 
%% The produced rules achieved a detection rate up to 96\%, the false positive rate 
%% was not evaluated. 
%% 
%% On our experiments with Syrius, we used a total of \totalPackets packets that 
%% matches \totalAttacks different existing rules and it was able to generate rules that detected 
%% all the packets with no false positives.  
%%  }  
\subsubsection{Running time}\Mar{}\Gui{We ran all our tests using an Intel(R) Xeon(R) CPU E3-1240 v6 and 8GB RAM. For attacks with only categorical and numerical options, the average running time was 6 seconds per attack. For attacks with the content option, the average running time was 1445 seconds.}

@@

\Gui{Ganesan \etal{}\cite{ganesan} introduces an idea of generating new sets of rules based on modifications of existing rules. They used the community edition of snort rules from 2012 for the modifications and tested with the the pcap file from the MACCDC 2012 dataset. It was reported an increase in the number of alerts, but it wasn't analysed the false alarmrates for abduced rules. Their technique is parallel to the rule creation strategies, as the objective of the modified rules is to capture variations and evolutions of attacks.}
